---
title: "Dongsha Migrate Analysis"
output: html_notebook
---

Here is code that I used to set up migrate analyses on datasets from Dongsha atoll. These data are from samples that were collected by Rob Toonen, Michelle Gaither, Vanson Liu and Hawis Maduppa. The data themselves were largely generated by students in the BIO 444 class, and these students also set up the initial migrate runs for their class project. To do so they downloaded data from their species from GeOMe and picked 4-5 closest populations and set up several hypotheses about the best metapopulation model. I am now just taking those runs and re-running them twice more as migrate does not always converge well on a marginal likelihood for a model.

At first 

# Setting up the runs

## Renaming parmfiles
At first I was just going to set up a screen for each run and run them all manually, but decided to write a script to rename the parmfiles uniformly. It finds files with the word "Parmfile" in them and then renames them to "parmfile"
```{bash parmfile_namer.sh}
#!
for d in */
        do
          cd $d
          echo $d
                for f in $(find ./ -maxdepth 1 -type f -exec grep -l 'Parmfile' {} \;)
                 do 
                         mv $f parmfile
                 done
          cd ..
        done  
 

```

I then deleted all the PDF outfiles from the directories to mark each directory as new (I had copied directories with finished analyses)
```{bash}
 find . -type f -iname "*.pdf" -delete
```

## Script to set up runs
I used the following script to automagically set up a screen and run migrate in each sub-directory
```{bash screen_migrate.sh}
#!
#for s in */
#do
#       cd $s

        for m in */
        do
                cd $m
                echo $m
                screen -d -m migrate-n
                cd ..
        done
#       cd ..
#done
```

So now "Round 2" of these runs is off and running. I'll wait a week to check in and start round 3.

8/23/18

Finished Round 3

## Renaming Outfiles

Rename outfiles like so
```{bash}
#!
for d in */
        do
          cd $d
          echo $d
                for f in $(find ./ -maxdepth 1 -type f -exec grep -l 'Options in use' {} \;)
                 do 
                         mv $f outfile.txt
                 done
          cd ..
        done  
  
#And wrap that up in a loop

M053-303-26932:dongsha1 cran5048$ for e in */
> do
> cd $e
> echo $e
> bash ../../outfile_renamer.sh
> cd ..
> done

```

# Processing output

## Function for bayes factor calculations
```{r bfcalcs}
# a function for calculating model selection statistics
bfcalcs<-function(df,ml="bezier.corrected"){
  df$thermodynamic<-as.numeric(df$thermodynamic)
  df$bezier.corrected<-as.numeric(df$bezier.corrected)
  df$harmonic<-as.numeric(df$harmonic)
    mlcol<-df[,ml] 
	bmvalue<-mlcol[which.max(mlcol)]
	lbf<-2*(mlcol-bmvalue)
	choice<-rank(-mlcol)
	modelprob<-exp(lbf/2)/sum(exp(lbf/2))
	dfall<-cbind(df,lbf,choice,modelprob)
	return(dfall)
}	
```


## Harvesting Likelihoods

```{r harvest_likelihoods}
wd<-"~/Datasets/dongsha/"
setwd(wd)

m<-c("panmixia","n_island","dongsha_sink","dongsha_source","stepping_stone")



likelists<-list()
for(r in 1:3){
  wd1<-paste(wd,"dongsha",r,sep="")
  setwd(wd1)
  # start here if you just want to do one list
  likelist<-list() #initialize an empty list
  for(f in list.files()){
    wd2<-file.path(wd1,f)
    marglike<-data.frame(model=character(0),thermodynamic=numeric(0),bezier.corrected=numeric(0),harmonic.mean=numeric(0),stringsAsFactors=F) #initialize a data frame to take the values
    l=1 #initialize l
    for(i in m){ #i<-"stepping_stone"
      wd3<-file.path(wd2,i)
      print(wd3)
      if(!file.exists(wd3)){next}
      setwd(wd3)
      outfile<-scan(file="outfile.txt",what="character",sep="\n") #scan in the outfile, separating at each newline
      
      #get the result from thermodynamic integration
      thermoline<-grep("(1a)",outfile,value=T) #find the line with the thermodynamic likelihood on it
      if(length(thermoline)==0){next}
      thermoline<-strsplit(thermoline,split="=",fixed=T) #split it up
      thermo<-as.numeric(substr(thermoline[[1]][2],start=1,stop=12)) #grab the thermodynamic likelihood
      bezistart<-grep("\\(",strsplit(thermoline[[1]][2],split="")[[1]])+1
      bezier<-as.numeric(substr(thermoline[[1]][2],start=bezistart,stop=bezistart+11)) #and the bezier-corrected value
      #get the harmonic mean
      harmoline<-grep("\\(2\\) H",outfile,value=T) #find the line with harmonic mean likelihood on it
      harmoline<-strsplit(harmoline,split="=",fixed=T) #grab the harmonic mean
      harmo<-as.numeric(substr(harmoline[[1]][2],start=1,stop=12))
      marglike[l,]<-c(i,thermo,bezier,harmo) #add this as a row to the data frame
      l=l+1
    }
    

    
    likelist[[f]]<-marglike #add the dataframe to the list
  }
  
# stop here if you just want one round  
  likelists[[r]]<-likelist
}
setwd(wd)
```

## Model Selection
On each round, and then bind them into a list
```{r model_selection}
modeltable1<-lapply(likelists[[1]],bfcalcs)
modeltable2<-lapply(likelists[[2]],bfcalcs)
modeltable3<-lapply(likelists[[3]],bfcalcs)
modeltables<-list("round1"=modeltable1,"round2"=modeltable2,"round3"=modeltable3)

head(modeltables[[1]],1)
```

## Plot marginal likelihood results from each of 3 runs
```{r}
library(ggplot2)
setwd(wd)
speciesnames<-read.csv("species_names.csv")

pdf(file = "thermodynamic_marginal_likelihoods_final.pdf",width=8.5,height=3)
means<-list()
#plots<-list()
for(dataset in names(modeltables[[1]])){
  likes<-rbind(cbind(modeltables[[1]][[dataset]],rep=1), cbind(modeltables[[2]][[dataset]],rep=2), cbind(modeltables[[3]][[dataset]], rep=3))
  likes$model<-factor(likes$model, m)
  likes<-likes[!(is.na(likes$model)),]
  
speciesname<-speciesnames$Species[which(speciesnames$Working==dataset)]
  
  #likes<-likes[which(likes$bezier.corrected > max(likes$bezier.corrected)-100),]
  y.mean<-as.vector(by(likes$bezier.corrected,likes$model,mean))
  y.sd<-as.vector(by(likes$bezier.corrected,likes$model,sd))
  y.min<-y.mean-((y.sd/sqrt(3))*4.303)
  y.max<-y.mean+((y.sd/sqrt(3))*4.303)

    
  likes.mean<-data.frame(model=factor(m,m),y.mean,y.min,y.max,y.sd)
  means[[dataset]]<-likes.mean
  
  #l<-ggplot(data=likes, aes(x=model,y=bezier.corrected,colour=factor(rep), 
   #                                 shape=factor(rep), size=20 ))
  l<-ggplot(data=likes, aes(x=model,y=bezier.corrected))
  
  l<-l+geom_point(colour="blue", size=3)+
    geom_pointrange(data=likes.mean,y=y.mean,ymin=y.min,ymax=y.max, size=0.5)+
    scale_x_discrete(drop=FALSE)+
    theme(axis.text.y = element_text(size=16),legend.position="none",axis.title.x=element_text(size=16),axis.title.y=element_blank(),plot.title=element_text(size=20))+ggtitle(speciesname)+ylab("Marginal Log-Likelihood")+
    coord_fixed(0.1)+ coord_flip()
  print(l)
#  plots<-c(plots,l)
}
dev.off()


```
## Take the mean marginal likelihoods over three runs and calculate model selection tables.
```{r}
library(perm)

meanlikes<-list()
permtests<-data.frame(matrix(ncol = 10, nrow = 0))
colnames(permtests)<-c(m,"k-means p-value","Best Mean","Second Best Mean","p-value Best Mean > Second Mean", "Log Bayes Factor")

for(dataset in names(modeltables[[1]])){
  likes<-rbind(cbind(modeltables[[1]][[dataset]],rep=1), cbind(modeltables[[2]][[dataset]],rep=2), cbind(modeltables[[3]][[dataset]], rep=3))
  likes$model<-factor(likes$model, m)
  likes<-likes[!(is.na(likes$model)),]
  likes$model<-factor(likes$model, m)
  y.mean<-as.vector(by(likes$bezier.corrected,likes$model,mean)) #take the means for each model
  kmeans.p<-permKS(x = likes$bezier.corrected, g = likes$model, method="exact.mc")$p.value #k-means non-parametric test to compare all means
  bestmean<-m[order(y.mean,decreasing=T)[1]] # get the highest mean
  secondmean<-m[order(y.mean,decreasing=T)[2]] #get the second best mean
  ttest<-permTS(x=likes$bezier.corrected[which(likes$model==bestmean)], y=likes$bezier.corrected[which(likes$model==secondmean)], alternative="greater", method="exact.mc")
  lbf<-2*ttest$estimate
  
  values<-rbind(y.mean)
  values<-cbind(values,kmeans.p,bestmean,secondmean,ttest$p.value,lbf)
  
  permtests[dataset,]<-values

	bmvalue<-y.mean[which.max(y.mean)]
	lbf<-2*(y.mean-bmvalue)
	modelrank<-rank(-y.mean)
	modelprob<-exp(lbf/2)/sum(exp(lbf/2),na.rm=T)
	dfall<-cbind("Mean Bezier Corrected ML"=as.numeric(y.mean),"LBF"=as.numeric(lbf),"Rank"=as.numeric(modelrank),"Model_Probability"=as.numeric(modelprob))
	row.names(dfall)<-m
	dfall<-as.data.frame(dfall)
	meanlikes[[dataset]]<-dfall
  
}
```

## Calculate the best models table and save it
```{r}
getmodels2<-function(dfr){
  model1<-row.names(dfr)[which(dfr$Rank==1)]
  model2<-row.names(dfr)[which(dfr$Rank==2)]
  modelprob1<-dfr$Model_Probability[which(dfr$Rank==1)]
  modelprob2<-dfr$Model_Probability[which(dfr$Rank==2)]
  print(model1)
  print(model2)
  print(modelprob1)
  c(model1,modelprob1,model2,modelprob2)
}

bestmodeltable<-lapply(meanlikes,getmodels2)
bestmodeltable<-t(as.data.frame(bestmodeltable))
colnames(bestmodeltable)<-c("bestmodel","bestmodelprob","secondbestmodel","secondbestmodelprob")
bestmodeltable<-cbind(bestmodeltable,permtests[6],permtests[9])


write.csv(bestmodeltable,file="Final_BestModeltable_Using_Means_of_3reps.csv")
write.csv(permtests,file="Permutation_ttest_results.csv")
save(meanlikes,file="Final_Modeltable_Using_Means_of_3reps.R")
```


## Plot Model Probability

```{r model_probability}

#read in the t-test results
#tt<-read.table(file="~/Dropbox/Crandall_tobo/scripts/Final_BestModeltable_Using_Means_of_3reps.csv",header=T,sep=",")

means<-data.frame(dataset=character(),species=character(),common=character(),models=character(),modelprob=numeric())
#names<-read.csv("Species_names.csv", stringsAsFactors = F)

for(dataset in names(modeltables[[1]])){
  #make a long dataset of model probabilities from each dataset
  species<-speciesnames[which(speciesnames$Working==dataset),2] #lookup the species name

  likes<-rbind(cbind(modeltables[[1]][[dataset]],rep=1), cbind(modeltables[[2]][[dataset]],rep=2), cbind(modeltables[[3]][[dataset]], rep=3))
  likes$model<-factor(likes$model, m)
  likes<-likes[!(is.na(likes$model)),]
  #take the mean model probability
  y.mean<-as.vector(by(likes$modelprob,likes$model,mean))
  #put this back in a data frame with model
  likes.mean<-data.frame(dataset=dataset,species=species,model=factor(m,m),modelprob=y.mean)
  means<-rbind(means,likes.mean)
}

#CODE FOR SORTING SPECIES
#take the value for stepping stone from each model and sort on it
#species<-unique(as.character(means$species)) #make a character vector of all species

#set mean probs for stepping stone that are less than 0.01 to 0 so I can also sort on panmixia
#means[means$model=="stepping.stone" & means$modelprob<0.01,"modelprob"]<-0
#sort it by value of stepping.stone
#species2<-species[order(-tt$ttest_pvalue, #means[means$model=="stepping.stone","modelprob"], #means[means$model=="stepping.stone.1param","modelprob"],
#means[means$model=="hi_lo","modelprob"],
#means[means$model=="empirical","modelprob"],
#means[means$model=="n.island","modelprob"],
#                        decreasing=T)] 
#
#means$model<-factor(means$model,levels=m,labels=c("k <= 14, Stepping-Stone, ~40 parameter","k <= 14, Stepping-Stone, 2 parameter","k = 3, 2 Currents, 7 parameter","k = 2, 1 Current, 4 parameter", "k = 2, High/Low Islands, 4 parameter","k = ? Empirical Structure, ? parameter","k <= 14, n-Island, 2 parameter","k=1, Panmixia, 1 parameter"))

# This is the order I settled on - significant first.
#species2<-c("Cellana talcosa", "Ophiocoma pica", "Chaetodon miliaris", 
"Zebrasoma flavescens", "Caranx melampygus", "Heterocentrotus mammillatus", 
"Mulloidichthys vanicolensis", "Panulirus penicillatus", "Calcinus hazletti", 
"Chaetodon multicinctus", "Chaetodon lunulatus", "Holothuria atra", 
"Cellana exarata", "Holothuria whitmaei", "Halichoeres ornatissimus", "Acanthurus olivaceus","Gymnothorax flavimarginatus","Squalus mitsukurii", 
"Abudefduf abdominalis", "Mulloidichthys flavolineatus", "Stenella longirostris", "Panulirus marginatus",
"Chaetodon fremblii", "Calcinus seurati", "Epinephelus quernus", "Lutjanus kasmira", 
"Acanthurus nigroris",  "Etelis marshi", "Parupeneus multifasciatus", "Ctenochaetus strigosus","Triaenodon obesus", "Abudefduf vaigiensis", "Stegastes fasciolatus", 
"Pristipomoides filamentosus", "Cellana sandwicensis", "Dascyllus albisella", 
"Acanthurus nigrofuscus", "Acanthaster planci", "Ophiocoma erinaceus", 
"Gymnothorax undulatus", "Myripristis berndtii")

#means$species<-factor(means$species,levels=species2)
means$model<-factor(means$model,levels=m,labels=c("Panmixia","N-Island","Dongsha Sink","Dongsha Source", "Stepping-Stone"))

library(ggplot2)
library(RColorBrewer)

my.cols<-brewer.pal(8,"RdYlBu")
my.cols[8]<-"#7f7f7f"
my.cols[5]<-"#FFFFBF"
my.cols[6]<-"#FFFF00"


mprobs<-ggplot(data=means,mapping=aes(x=species,y=modelprob,fill=model)) + 
  geom_bar(stat="identity") + scale_fill_manual(values=my.cols, guide = guide_legend(title = "Migrate Models")) + 
  theme(axis.text.x=element_text(angle=90, hjust=1,vjust=0.5, color=c(rep("grey25",26),rep("grey70",15))), legend.text = element_text(size = 14), legend.title = element_text(size = 20), axis.text.y= element_text(size = 14), axis.title.y=element_text(size=14)) +
  scale_y_continuous(name="Model Probability") + scale_x_discrete(name="Species")

mprobs

ggsave(filename = "dongsha_bars_final_landscape.pdf", width = 8, height=6,units = "in")
```
